Machine Learning Methods for Discourse Segmentation of E-Mail Based Clinical Communication

### 2018-03-09 paper-amia-2018/manuscript.tex
merged with alex

\section*{Methods}
\subsection*{\textit{Data collection}}
The experimental dataset for this work was constructed from 49 e-coaching sessions, which include a total of 3,138 segmented and annotated MI behaviors. Each session represents an MI intervention delivered via email. To filter out noise from the dataset, non-ascii characters are removed and then applied stemming to obtain a general form of word from different word representations, such as ``eating'', ``eats'', and ``eat''. We formulate the text segmentation task into a binary classification, as shown in Figure~\ref{fig:classifier}. Clinical exchange is given as the input, it is partitioned as adjacent word pairs by sliding them. Each pair is classified into either ``boundary'' or ``not boundary'' class. The original text is segmented at the position, where an adjacent word pair classified into ``boundary'' class. If all adjacent pairs of a block of text classified into ``not boundary'', the whole block of text is then treated as one segment about a single MI behavior. Totaly, we obtained 95,421 word pairs, which include 3,138 ``boundary'' and 92,283 ``not boundary'' instances.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.80\textwidth]{figures/classifier.png}
    \caption{\textbf{Transformation of text segmentation task into text classification task}.}
    \label{fig:classifier}
\end{figure}

For the experiment, we utilized three type of features including word (textual feature), topic, and punctuation mark. Each word represented in a binary format, where 1 indicates the appearance of the word and 0 for absence. Topics are considered as features since topic models are very effective\cite{kotov2015interpretable,hashimoto2016topic,lu2016modeling} to represent text documents. In this paper, we exploit a topic model named Labeled LDA\cite{ramage2009labeled} model, where topics correspond to labels. The generative process of Labeled LDA drawing the multinomial topic distributions over vocabulary for each topic. In our experiment, we represent each word in a vector of 2 topics, where the number of topics is experimentally determined by the model performance\cite{kotov2015interpretable}. Punctuation mark containing one of the symbols \{`.', `,', `!', `?', `:', `;', `-'\} is also employed as feature. This is one of the most important features as they indicate the boundary of a sentence, clause, and phrase.

@@

\begin{equation}
z_t = \sigma(W_zx_t + U_zh_{t-1} + b_z)
\label{eq:firstgru}
\end{equation}
\begin{equation}
r_t = \sigma(W_rx_t + U_rh_{t-1} + b_r)
\label{eq:resetgru}
\end{equation}
\begin{equation}
\tilde h_t = tanh(W_hx_t + r_t \odot U_hh_{t-1} + b_h) 
\label{eq:candidategru}
\end{equation}
\begin{equation}
h_t = z_t \odot h_{t-1} + (1-z_t) \odot \tilde h_t
\label{eq:lastgru}
\end{equation}  
In Eq.~\ref{eq:firstgru}-\ref{eq:lastgru}, $\sigma$ corresponds to sigmoid function and $\odot$ designates an element-wise product. The update gate $z_t$ and reset gate $r_t$ at time step $t$ are computed by the Eq.~(\ref{eq:firstgru}) and~(\ref{eq:resetgru}), where $W_z$, $W_r$, $W_h$, $U_z$, $U_r$, $U_h$ are the weight matrices and $b_z$, $b_h$ and $b_r$ are bias vectors. The activation $h_t$ of the GRU at time $t$ is a linear combination of previous activation $h_{t-1}$ and the candidate activation $\tilde h_t$, which is represented by Eq.~(\ref{eq:lastgru}) and~(\ref{eq:candidategru}). We build our RNN model with one hidden layer, output layer, and input layer. One segmented text was taken as input sequence which get one hot encoding of word vector for the model input. A binary label was assigned as output sequence where ``boundary'' and `not boundary'' words were associated with label 1 and 0, respectively. We reset our model state after feeding each input sequence. Since one-hot vector is given in the input layer, results are reported with textual and punctuation mark features only. We experimentally determined that the best performance is achieved when the number of hidden units = 25, batch size = 1, and optimizer = adam.

\subsection*{\textit{Evaluation metrics}}
In this experiment, standard metrics: precision, recall, and F1-measure, are applied to evaluate the performance of binary classifiers\cite{aas1999text}. However, accuracy is not reported as a performance metric because accuracy is highly sensitive to the prior class probabilities and does not fully describe the actual difficulty of the decision problem for an unbalanced dataset. We conduct the experiment with 5 folds cross-validation and weighted macro-averaging of these metrics over the folds. All models have trained on 80\% of the word pairs and remaining 20\% of the data is used as a test set for reporting the performance of the model. We also estimate the area under the receiving operating characteristics (ROC) curve\cite{kumar2011receiver} (AUC) metric due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets\cite{hu2015kernelized}.

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, KNN, and RNN methods for detecting segmentation boundary in e-coaching text. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_boundary}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{contextual features only}} & \multicolumn{3}{|c|}{\textbf{contextual + punctuation marks (+ topics except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure}\\ \hline

@@

As follows from Table~\ref{tab:result_boundary}, KNN performs best among all machine learning models in terms of precision and F1-measure, achieved 0.808 precision with 0.728 F1-measure when contextual features are used, and 0.820 precision with 0.779 F1-measure when a combination of contextual, topic, and punctuation mark features are used. However, NB demonstrates the lowest performance among all models in terms of all performance metrics. In this study, GRU appears as the second highest model, obtains 10.68\% higher recall with 3.78\%  higher F1-measure than LSTM. On the other hand, SVM exhibits highest recall 0.679 when only textual features are used. When textual features are used in combination with topic and punctuation mark features, recall increases by 0.6\%, 2.5\%, and 11.92\%; and F1-measure increases by 0\%, 3.39\%, and 7\% for NB, SVM, and KNN models, respectively. Nevertheless, precision increases by 4.31\% and 1.49\% for SVM and KNN methods while decreases by 0.7\% in NB. \\

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, KNN, and RNN methods for the identification of ``not boundary'' class. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_not_boundary}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{contextual features only}} & \multicolumn{3}{|c|}{\textbf{contextual + punctuation marks (+ topics except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure}\\ \hline

@@

Table~\ref{tab:result_not_boundary} summarizes the performance of NB, SVM, KNN, and RNN models for detecting ``not boundary'' class in e-coaching text. We observed that performance is remarkably high in ``not boundary'' class compared to boundary detection which is expected because 96.71\% instances are from ``not boundary'' class. KNN achieves 22.40\%, 50.07\%, and 36.26\% higher precision, recall, and F1-measure for contextual features; and 20.85\%, 33.96\%, and 27.47\% higher precision, recall, and F1-measure for combined features compared to boundary class. In contrast to boundary detection, RNN demonstrates the highest performance among all models. LSTM obtains 0.993 precision with 0.994 recall and F1-measure while LSTM exhibits 0.994 for all performance metrics. Impact of additional features is also consistent with ``not boundary'' classification. Results show that F1-measure increases by 0\%, and 0.1\% for SVM and KNN models although decreases by 0.1\% for NB. \\

\begin{table}[ht]
\centering
\caption{Weighted average performance of NB, SVM, KNN, and RNN methods for the segmentation of e-coaching text in detecting both ``boundary'' and ``not boundary'' classes. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_weighted_avg}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{contextual features only}} & \multicolumn{3}{|c|}{\textbf{contextual + punctuation marks (+ topics except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure}\\ \hline

 NB & 0.975 & 0.974 & 0.975 & 0.976 & 0.974 & 0.975 \\ \hline
 SVM & 0.981 & 0.982 & 0.981 & 0.983 & 0.983 & 0.983\\ \hline
 KNN & \textbf{0.983} & \textbf{0.984} & 0.983 & \textbf{0.986} & \textbf{0.986} & \textbf{0.986}\\ \hline
 LSTM & -- & -- & -- & \textbf{0.986} & 0.983 & 0.984 \\ \hline
 GRU & -- & -- & -- & \textbf{0.986} & 0.985 & \textbf{0.986} \\ \hline 
  \end{tabular}
\end{table}

Table~\ref{tab:result_weighted_avg} outlines the weighted average results of the experiment on the models for the segmentation of e-coaching text by classifying them into ``boundary'' and ``not boundary'' classes. Overall, KNN obtains the best performance with all metrics and NB denotes the lowest performance among all methods. GRU demonstrates the same result as KNN for precision and F1-measure except for recall. SVM shows moderate performance, obtains 0.981, 0.982, and 0.983 for precision, recall, and F1-measure, respectively when textual features are used. Influence of the additional features is also consistent as above, precision increases by 0.1\%, 0.2\%, and 0.3\%; recall increases by 0\%, 0.1\%, and 0.2\%; and F1-measure increases by 0\%, 0.2\%, and 0.3\% for NB, SVM, and KNN methods, respectively, when combined features are used.\\

@@

The additional topic and punctuation mark feature made a significant improvement in performance of all machine learning methods. Nearly all cases, the model performs better when contextual features are used in combination with topic and punctuation mark features. This results also mean that segmentation performance might be improved by adding more relevant features including human insight into the problem.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/roc-curves.png}
    \caption{\textbf{Receiver operating characteristic curves showing the performance of binary classifiers for the segmentation of e-coaching text when textual features (left) and combination of textual and other features (right) are used}.}
    \label{fig:roc-curves}
\end{figure}

In this paper, results are reported by each class to avoid confusion about the overall model performance. In addition, standard metrics: precision, recall, and F1-measure were used to eliminate doubt about the model performance because accuracy is misleading for imbalance dataset. AUC values are also outlined due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets\cite{hu2015kernelized}, which are demonstrated by the ROC curves in Figure~\ref{fig:roc-curves}. NB shows the highest AUC values, achieved 0.978 for both cases while provides lowest classification results. On the other hand, KNN and SVM exhibit 0.972 and 0.835 AUCs when only textual features are used; and 0.959 and 0.844 AUCs when a combination of textual, topic and punctuation mark features are used. Finally, LSTM demonstrates lowest AUC values among all machine learning models, achieved 0.82 AUC while GRU achieves 4.15\% higher AUC than LSTM. The conclusion drawn from the ROC curves also confirmed the robustness and superiority of KNN model for the segmentation of clinical exchange.

We observed the second highest performance of RNN, in particular, LSTM and GRU for the text segmentation. We believe that RNN will perform better if a large set of data is utilized. In this study, we employed 3,138 examples of boundary case which failed to achieve best results. We also observed that GRU performs better than LSTM which was observed in other previous study\cite{chung2014empirical}.

>>>>

\section*{Methods}
\subsection*{\textit{Data collection}}
The experimental dataset for this work was constructed from 49 e-coaching sessions, which include a total of 3,138 segmented and annotated MI behaviors. Each session represents an MI intervention delivered via email. To filter out noise from the dataset, non-ascii characters are removed and then applied stemming to obtain a general form of word from different word representations, such as ``eating'', ``eats'', and ``eat''. We formulate the text segmentation task into a binary classification, as shown in Figure~\ref{fig:classifier}. For NB, SVM and KNN models, clinical exchange is given as the input then it is partitioned as adjacent word pairs by sliding them. Each pair is classified into either ``boundary'' or ``not boundary'' class. The original text is segmented at the position, where an adjacent word pair classified into ``boundary'' class. If all adjacent pairs of a block of text classified into ``not boundary'', the whole block of text is then treated as one segment about a single MI behavior. Totally, we obtained 95,421 word pairs, which include 3,138 ``boundary'' and 92,283 ``not boundary'' instances. For RNN, a chunk of text was taken as input sequence which gets one hot encoding of word vector for the model input. A binary label was assigned as output sequence where ``boundary'' and `not boundary'' words were associated with label 1 and 0, respectively.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.80\textwidth]{figures/classifier.pdf}
    \caption{\textbf{Transformation of text segmentation task into text classification task}.}
    \label{fig:classifier}
\end{figure}

For the experiment, we utilized three type of features including word (contextual feature), punctuation mark, and topic model-based features. In contextual features, each word represented in a binary format, where 1 indicates the appearance of the word and 0 for absence. Since topic models are very effective\cite{kotov2015interpretable,hashimoto2016topic,lu2016modeling} to represent text documents, we derived features from a topic model named Labeled LDA\cite{ramage2009labeled}. To obtain feature values, we utilize the experimental data which is segmented as MI code or class. First, we derived a class-specific multinomial $p(w|c)$ per each class $c$ from class-specific topics: $p(w|c, z)$ by marginalizing over topic z, where the number of topics is experimentally determined by the model performance\cite{kotov2015interpretable}.

$$p(w|c) = {\sum_{z=1}^{K}{p(w|z, c)}}$$

Here, $K$ is the number of topics per class $c$. After that, word-specific class distributions $p(c|w)$ were estimated with class-specific multinomials $p(w|c)$ by using the following formula:

$$p(c|w) = \frac{p(w|c)p(c)}{p(w)}$$

where $p(c)$ is the prior distribution of class $c$ in the training set and $p(w)$ is a probability of word $w$ in the collection language model estimated using maximum likelihood. In our experiment, we represent $p(c|w)$ as the feature showing that how indicative each word $w$ for a particular class $c$. Punctuation mark containing one of the symbols \{`.', `,', `!', `?', `:', `;', `-'\} is also employed as feature. This is one of the most important features as they indicate the boundary of a sentence, clause, and phrase.

@@

\begin{equation}
z_t = \sigma(W_zx_t + U_zh_{t-1} + b_z)
\label{eq:firstgru}
\end{equation}
\begin{equation}
r_t = \sigma(W_rx_t + U_rh_{t-1} + b_r)
\label{eq:resetgru}
\end{equation}
\begin{equation}
\tilde h_t = tanh(W_hx_t + r_t \odot U_hh_{t-1} + b_h) 
\label{eq:candidategru}
\end{equation}
\begin{equation}
h_t = z_t \odot h_{t-1} + (1-z_t) \odot \tilde h_t
\label{eq:lastgru}
\end{equation}  
In Eq.~\ref{eq:firstgru}-\ref{eq:lastgru}, $\sigma$ corresponds to sigmoid function and $\odot$ designates an element-wise product. The update gate $z_t$ and reset gate $r_t$ at time step $t$ are computed by the Eq.~(\ref{eq:firstgru}) and~(\ref{eq:resetgru}), where $W_z$, $W_r$, $W_h$, $U_z$, $U_r$, $U_h$ are the weight matrices and $b_z$, $b_h$ and $b_r$ are bias vectors. The activation $h_t$ of the GRU at time $t$ is a linear combination of previous activation $h_{t-1}$ and the candidate activation $\tilde h_t$, which is represented by Eq.~(\ref{eq:lastgru}) and~(\ref{eq:candidategru}). We build our RNN model with one hidden layer, output layer, and input layer. We reset our model state after feeding each input sequence where input was given as one-hot encoding of word vector. Since one-hot vector is given in the input layer, results are reported with contextual and punctuation mark features only. We experimentally determined that the best performance is achieved when the number of hidden units = 25, batch size = 1, and optimizer = adam.

\subsection*{\textit{Evaluation metrics}}
In this experiment, standard metrics: precision, recall, and F1-measure, are applied to evaluate the performance of binary classifiers\cite{aas1999text}. However, accuracy is not reported as a performance metric because accuracy is highly sensitive to the prior class probabilities and does not fully describe the actual difficulty of the decision problem for an unbalanced dataset. We conduct the experiment with 5 folds cross-validation and weighted macro-averaging of these metrics over the folds. All models have trained on 80\% of the data and remaining 20\% of the data is used as a test set for reporting the performance of the model. We also estimate the area under the receiving operating characteristics (ROC) curve\cite{kumar2011receiver} (AUC) metric due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets\cite{hu2015kernelized}.

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, KNN, and RNN methods for detecting segmentation boundary in e-coaching text. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_boundary}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{contextual features only}} & \multicolumn{3}{|c|}{\textbf{contextual + punctuation marks (+topic-based except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure}\\ \hline

@@

As follows from Table~\ref{tab:result_boundary}, KNN performs best among all machine learning models in terms of precision and F1-measure, achieved 0.808 precision with 0.728 F1-measure when contextual features are used; and 0.820 precision with 0.779 F1-measure when a combination of contextual, punctuation mark and topic model-based features are used. However, NB demonstrates the lowest performance among all models in terms of all performance metrics. In this study, GRU appears as the second highest model, obtains 10.68\% higher recall with 3.78\%  higher F1-measure than LSTM. On the other hand, SVM exhibits highest recall 0.679 when only contextual features are used. When contextual features are used in combination with punctuation mark and topic model-based features, recall increases by 0.6\%, 2.5\%, and 11.92\%; and F1-measure increases by 0\%, 3.39\%, and 7\% for NB, SVM, and KNN models, respectively. Nevertheless, precision increases by 4.31\% and 1.49\% for SVM and KNN methods while decreases by 0.7\% in NB. \\

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, KNN, and RNN methods for the identification of ``not boundary'' class. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_not_boundary}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{contextual features only}} & \multicolumn{3}{|c|}{\textbf{contextual + punctuation marks (+ topic-based except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure}\\ \hline

@@

Table~\ref{tab:result_not_boundary} summarizes the performance of NB, SVM, KNN, and RNN models for detecting ``not boundary'' class in e-coaching text. We observed that performance is remarkably high in ``not boundary'' class compared to boundary detection which is expected because 96.71\% instances are from ``not boundary'' class. KNN achieves 22.40\%, 50.07\%, and 36.26\% higher precision, recall, and F1-measure, respectively, for contextual features; and 20.85\%, 33.96\%, and 27.47\% higher precision, recall, and F1-measure, respectively, for combined features compared to boundary class. In contrast to boundary detection, RNN demonstrates the highest performance among all models. LSTM obtains 0.993 precision with 0.994 recall and F1-measure while GRU exhibits 0.994 for all performance metrics. Impact of punctuation mark and topic model-based features is also consistent with ``not boundary'' classification. Results show that F1-measure increases by 0\%, and 0.1\% for SVM and KNN models although decreases by 0.1\% for NB. \\

\begin{table}[ht]
\centering
\caption{Weighted average performance of NB, SVM, KNN, and RNN methods for the segmentation of e-coaching text in detecting both ``boundary'' and ``not boundary'' classes. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_weighted_avg}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{contextual features only}} & \multicolumn{3}{|c|}{\textbf{contextual + punctuation marks (+ topic-based except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure}\\ \hline

 NB & 0.975 & 0.974 & 0.975 & 0.976 & 0.974 & 0.975 \\ \hline
 SVM & 0.981 & 0.982 & 0.981 & 0.983 & 0.983 & 0.983\\ \hline
 KNN & \textbf{0.983} & \textbf{0.984} & \textbf{0.983} & \textbf{0.986} & \textbf{0.986} & \textbf{0.986}\\ \hline
 LSTM & -- & -- & -- & \textbf{0.986} & 0.983 & 0.984 \\ \hline
 GRU & -- & -- & -- & \textbf{0.986} & 0.985 & \textbf{0.986} \\ \hline 
  \end{tabular}
\end{table}

Table~\ref{tab:result_weighted_avg} outlines the weighted average results of the experiment on the models for the segmentation of e-coaching text by classifying them into ``boundary'' and ``not boundary'' classes. Overall, KNN obtains the best performance with all metrics and NB denotes the lowest performance among all methods. GRU demonstrates the same result as KNN for precision and F1-measure except for recall. SVM shows moderate performance, obtains 0.981, 0.982, and 0.983 for precision, recall, and F1-measure, respectively, when contextual features are used. Influence of the additional features is also consistent as mentioned in Table~\ref{tab:result_boundary} and~\ref{tab:result_not_boundary}. Precision increases by 0.1\%, 0.2\%, and 0.3\%; recall increases by 0\%, 0.1\%, and 0.2\%; and F1-measure increases by 0\%, 0.2\%, and 0.3\% for NB, SVM, and KNN methods, respectively, when combined features are used.\\

@@

Punctuation mark and topic model-based features made a significant improvement in performance of all machine learning methods. Nearly all cases, the model performs better when contextual features are used in combination with punctuation mark and topic model-based features. This results also mean that segmentation performance might be improved by adding more relevant features including human insight into the problem.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/roc-curves.png}
    \caption{\textbf{Receiver operating characteristic curves showing the performance of binary classifiers for the segmentation of e-coaching text when contextual features (left) and combination of contextual and other features (right) are used}.}
    \label{fig:roc-curves}
\end{figure}

In this paper, results are reported by each class to avoid confusion about the overall model performance. In addition, standard metrics: precision, recall, and F1-measure were used to eliminate doubt about the model performance because accuracy is misleading for imbalance dataset. AUC values are also outlined due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets\cite{hu2015kernelized}, which are demonstrated by the ROC curves in Figure~\ref{fig:roc-curves}. NB shows the highest AUC values, achieved 0.978 for both cases while provides lowest classification results. On the other hand, KNN and SVM exhibit 0.972 and 0.835 AUCs when only contextual features are used; and 0.959 and 0.844 AUCs when a combination of contextual, punctuation mark and topic model-based features are used. Finally, LSTM demonstrates lowest AUC values among all machine learning models, achieved 0.82 AUC while GRU achieves 4.15\% higher AUC than LSTM. The conclusion drawn from the ROC curves also confirmed the robustness and superiority of KNN model for the segmentation of clinical exchange.

We observed the second highest performance of RNN, in particular, LSTM and GRU for the text segmentation. We believe that RNN will perform better if a large set of data is utilized. In this study, we employed 3,138 examples of boundary case which limit to achieve the best performance. We also observed that GRU performs better than LSTM which was observed in other previous study\cite{chung2014empirical}.
